Transition path sampling and the calculation of free energies of enzymatic reactions

### 2022-03-29 tex/manuscript.tex
added Make file

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Atomistic level study of the mechanism of enzyme catalysis is necessary
to understand the efficiency of enzymes as well as to device strategies for inhibiting 
their activity. 
Transition path sampling \cite{Bolhuis02AnnRevPhysChem53p291,Dellago98JChemPhys108p1964}
is an unbiased monte carlo method in the trajectory space which is used for the calculation 
of reaction coordinates and transition states of complex chemical reactions. 
TPS uses reactive trajectories which connect a reactant state to a product state and these 
trajectories are rare in molecular dynamics simulations because of the energy 
barriers separating the reactants and the products. To overcome these energy barriers and 
to obtain ergodic sampling several methods have been developed over the years such as 
umbrella sampling, \cite{Kastner11WileyInterdiscipRevComputMolSci1p932} metadynamics, \cite{Barducci11WileyInterdiscipRevComputMolSci1p826}
steered MD, \cite{Park04JChemPhys120p5946}
milestoning, etc. These methods rely on applying bias
potentials for the system to overcome energy barriers and hence require the knowledge of 
the reaction coordinates.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Atomistic level detailed study of the mechanism of enzyme catalysis 
reactions is necessary to understand their efficiency as well as to 
design molecules that can act as inhibitors for their activity. 
Molecular dynamics (MD) simulations 2 have often been used to study 
large biomolecular systems in atomistic detail since they provide an 
excellent computational cost to detail ratio. MD simulations to study 
chemical reactions that go through free energy barriers are often 
impractical to simulate since it would take a long time for the system 
to cross over barriers.
To overcome these energy barriers and 
to obtain ergodic sampling several methods have been developed over the years such as 
umbrella sampling, \cite{Kastner11WileyInterdiscipRevComputMolSci1p932} 
metadynamics, \cite{Barducci11WileyInterdiscipRevComputMolSci1p826}
steered MD, \cite{Park04JChemPhys120p5946}
milestoning, etc. These methods rely on applying bias
potentials for the system to overcome energy barriers and hence require the knowledge of 
the reaction coordinates.  
Transition path sampling \cite{Bolhuis02AnnRevPhysChem53p291,Dellago98JChemPhys108p1964}
(TPS) is an enhanced sampling method for 
rare events that transition a system between two stable states often 
referred to as reactants and products. 6

TPS focuses on transition paths and not on stable states which introduces 
biases in the sampling of equilibrium distribution of the reaction coordinate.
